% arara: lualatex: { shell: true, interaction: nonstopmode }
% arara: makeglossaries
% arara: biber
% arara: lualatex: { shell: true, interaction: nonstopmode }
% arara: lualatex: { shell: true, interaction: nonstopmode }

\providecommand{\toplevel}{../..}
\providecommand{\importPath}{\toplevel/Shared/Imports}
\providecommand{\assetPath}{\toplevel/Assets}
\providecommand{\sharedPath}{\toplevel/Shared}

\documentclass[hidelinks]{article}

\input{\importPath/preamble}
\input{\importPath/glossary}
\input{\importPath/symbols}

\begin{document}
    \section{The \LaTeX~Family Tree}
        The \TeX~family tree is a large one. You will often see many of these terms thrown around and it can be difficult to make sense of it.
        The tree shown in Figure \ref{fig:texfamilytree} shows how each of the major active \TeX~siblings relate.
        \ExecuteMetaData[\importPath/assets.tex]{texfamilytree}
        \subsection{\TeX}
            \TeX~is the original typsetting tool create by Donald Knuth in the 1980s.
        \subsection{\Hologo{pdfTeX}}
            \Hologo{pdfTeX} is an extension to the original \TeX~that enables the creation of PDF files.
        \subsection{\LaTeX}
            As mention \TeX~primitive are the real way of interacting with the \TeX~engine, but they are challenging to work with.
            \LaTeX~is a collection of macros that ease the use \TeX~and facilitate writing new packages.
        \subsection{\Hologo{XeTeX}}
            \Hologo{XeTeX} is a development on \TeX~that extends support for languages and glyphs beyond those using just the roman alphabet.
        \subsection{\Hologo{LuaTeX}}
            \Hologo{LuaTeX} is a recent and ongoing development which exposes the \TeX~primitives via the small and fast scripting language Lua.
            This has many benefits but can be effectively summarized as making it easier to code in \TeX.

    \section{Processing \TeX~Files}
        \subsection{Manually Processing Files}
            Processing a \TeX~file typically just means running the right programs in a certain order.
            Because of the sizing, number, and ordering work \LaTeX~is doing during the compilation, it needs to be run at least twice.
            Typically if our document includes a bibliography (and other elements like glossaries or indices), the compilation procedure would mean executing each of the commands shown in Listing \ref{lst:compilation}.
            \begin{listing}[htbp]
                \begin{centering}
                    \begin{minted}{bash}
                        pdflatex --shell-escape --interaction=nonstopmode report
                        biber report
                        makeglossaries report
                        pdflatex --shell-escape --interaction=nonstopmode report
                        pdflatex --shell-escape --interaction=nonstopmode report
                    \end{minted}
                    \caption{Shell commands needed to compile a report directly}
                    \label{lst:compilation}
                \end{centering}
            \end{listing}
            A neat detail of these commands is that they can accept any \LaTeX~commands.
            This gives the possibility of changing variables in a document during the execution (see Listing \ref{lst:compilationwithcommands}).
            \begin{listing}[htbp]
                \begin{centering}
                    \begin{minted}{bash}
                        lualatex --shell-escape --interaction=nonstopmode "\\providecommand{\\iswhichmode}{draft}\\input{report}"
                        biber report
                        makeglossaries report
                        lualatex --shell-escape --interaction=nonstopmode "\\providecommand{\\iswhichmode}{draft}\\input{report}"
                        lualatex --shell-escape --interaction=nonstopmode "\\providecommand{\\iswhichmode}{final}\\input{report}"
                    \end{minted}
                    \caption{Shell commands compiling a document with addition commands provided at compile time}
                    \label{lst:compilationwithcommands}
                \end{centering}
            \end{listing}

        \subsection{latexmk}
            latexmk is a tool that tries to automate the latex compilation process by reading in the log files and figuring out what additional programs need to be run, and when to rerun the compilation.
            It is a very effective tool and in most cases the defacto \LaTeX~compiler.
            \begin{listing}[htbp]
                \begin{centering}
                    \begin{minted}{bash}
                        latexmk -pdf report.tex
                    \end{minted}
                    \caption{Shell command for compiling with latexmk}
                    \label{lst:latexmkcommands}
                \end{centering}
            \end{listing}

        \subsection{arara}
            Sometimes however, latexmk doesn't know of some additional tool or new intermediate program that needs to be run, and this can create issues.
            It is also at times trying to be too smart, and ends up creating issues.
            For these reasons my go-to for a number of years has been ARARA, a compilation tool that allows you to define the compilation process at the beginning of your document.
            Listing \ref{lst:araradirectives} shows the directive syntax for arara, with Listing \ref{lst:araracompilation} showing the actual command.
            \begin{listing}[H]
                \begin{centering}
                    \begin{minted}{latex}
                        % arara: lualatex: { shell: true, interaction: nonstopmode }
                        % arara: makeglossaries
                        % arara: biber
                        % arara: lualatex: { shell: true, interaction: nonstopmode }
                        % arara: lualatex: { synctex: true, shell: true, interaction: nonstopmode }
                    \end{minted}
                    \caption{Shell command for compiling with Arara}
                    \label{lst:araradirectives}
                \end{centering}
            \end{listing}
            \begin{listing}[H]
                \begin{centering}
                    \begin{minted}{bash}
                        arara -v report.tex
                    \end{minted}
                    \caption{Shell command for compiling with Arara}
                    \label{lst:araracompilation}
                \end{centering}
            \end{listing}

    \section{\TeX~Distributions}
        \TeX~and \LaTeX~is a very large collection of programs and files, and installing them each individually would be a huge hassle.
        Thankfully the programs and packages are available bundled together as a single distribution.
        The distribution of choice where possible is TeXLive.
        On Linux systems it is always available in the systems package manager.
        For Mac and Windows systems, there are a few different options because sometimes it can be challenging to get TeXLive to operate (though I have no personal experience with these).
        \subsection{Mac}
            \begin{itemize}
                \item TeXLive
                \item MacTeX
            \end{itemize}
        \subsection{Windows}
            \begin{itemize}
                \item TeXLive
                \item MiKTeX
                \item ProTeXt
            \end{itemize}

    \clearpage
    \standaloneBib
\end{document}
